\section{Agile Software Development}
\label{sec:Agile Software Development}

Means any software development approach, based and guided by \index{Agile Software Development}agile principles~(\url{http://agilemanifesto.org/}).

Warning, based on agile \emph{Principles}, not Methodologies. 

There is a huge difference between \emph{Principles}:
\begin{quote}
\texttt{I will not tolerate then someone will have no answer to a question, I will try to explain it immediately. I don't know how I will do it, I can use Jira tickets, email, Skype, personal visits, this doesn't matter.}
\end{quote} 
and a \emph{Methodology}:
\begin{quote}
\texttt{Everybody shut up! From now every person, who will need my answer to any question, should:}
\begin{enumerate}
\item 
\texttt{formulate his question shortly and briefly (link to a guide)},

\item
\texttt{raise an issue in Jira using a 'Question' template (link to a guide)},

\item
\texttt{assign it to the appropriate person,}

\item 
\texttt{mention his QA Lead and Test Manager in watchers mandatory.}
\end{enumerate}
\end{quote} 

Feel free to feel the difference.

Yes, the 'Agile methodology' does not exist.

\begin{quote}
The same with \index{SCRUM}SCRUM [p.\pageref{sec:SCRUM}]~\textemdash~this is not a methodology too, this is a software development \emph{framework} (a common strategy) for managing product development, driven by agile principles. 

You can drive a development process by SCRUM framework, used only \emph{over} a Methodology.
\end{quote} 

A lot of people wants to know about 'Agile' only '\textit{You will always have a working product delivered}' (Lies!) or '\textit{We can easily rework any issue, just tell us what to do}' (Deliberate lies!) , or '\textit{True agile testers didn't use test cases!}' (Kill this bastard!), or '\textit{We will have no requirements, because we are Agile, aren't we?}' (Not enough bullets\ldots) and didn't care about how such goals will be achieved. This can drive the project to the hell, but we are brave enough to getting things done, aren't we?
