\section{Security Testing}
\label{sec:Security Testing}

\index{Security Testing}Usually — a process intended to reveal flaws in the security mechanisms of an information system that protect data and maintain functionality as intended.

It looks like a simple 'Let's find some possibility to stole credit card numbers from our shop!' approach, but in fact Security Testing represent a totally different approach than testing some functionality, involving a lot of programming skills. Usually it looks like someone explore/decompile a program and write his own program for explore and decompile others.

\begin{quote}
 If you are bored for a little by \index{Functional Testing}Functional Testing, and you are looking for something else, then Security is the latest area for you. This is a whole profession, whis involve a lot of programming and administration servers skills and knowledge.
\end{quote} 

Well, winter is coming\ldots Let prepare for cold times. Are we enough strong for say 'Hello!' to winter? Are our bodies prepared for that?

Imagine a simple Doctor. At university he studied the human body, starting with cutting the frogs in the school laboratory, and then progressively started the autopsy of human bodies in the dissecting room.

Now suppose yourself. Do you know about medicine something more than 'If I'll get a chill, I will drink a hot tea with lemon and Aspirin!?

Feel the difference?

Who can effectively suppose/assume/find some weaknesses in human body? You, with tea and Aspirin, or a Doctor, who has killed during his university ages more frogs than you saw movies with \index{Bruce Lee}Bruce Lee?

Only just because it is called 'testing' (exactly like 'Functional Testing'!), each year a new generation of junior-jedi testers tries to study 'something new in testing'.

To succeed in security testing, it is necessary not only to understand how something is built, but why someone made certain technical decisions.